\documentclass[letterpaper,11pt]{article}

% \usepackage[style=ieee,url=false,doi=false,maxbibnames=99,sorting=ydnt,dashed=false,backend=biber]{biblatex}

\usepackage[style=ieee,url=true,doi=true,maxbibnames=99,sorting=none,dashed=false,backend=biber]{biblatex}

\usepackage{geometry}  
\geometry{a4paper,left=25mm,right=20mm,top=40mm,bottom=25mm}
\usepackage{pageslts,refcount}
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\bibliography{references_cv}
\usepackage{simplecv}

\cfoot{\thepage\ of \pageref{LastPage}}               
\rfoot{\ifnum\getpagerefnumber{VeryLastPage}=\value{page} \textit{Last Updated: \today} \fi}

\begin{document}

% Heading
\headinginline{Saurabh Kumar}{
    Google Scholar: \website{tinyurl.com/4pyub4pd} \\
    GitHub: \github{saurabhk0317} \\
    Email: \email{saurabhk0317@gmail.com} \\
    LinkedIn: \linkedin{saurabhk0317}
}

\section{Education}
\textbf{National Institute of Technology, Patna} \hfill 2016\textendash 2020 \\
B.Tech. in Electronics and Communication Engineering \\
GPA: 7.42/10.00

\section{Experience}
\textbf{SPIRE Lab, IISc Bangalore, India} \hfill July 2021\textendash Present \\
Research Associate \\
Advisor: Prof. Prasanta Kumar Ghosh \\
Projects:
\begin{itemize}
  \item \href{https://respin.iisc.ac.in/}{\textbf{RESPIN}}: \textit{Speech Recognition in Agriculture and Finance for the Poor in India} \\
  Publications: \cite{kumar2025respins, Saurabh_IS25, ICASSP25_DID, IS24_ASR, ASRU23_RESPIN}
  \begin{itemize}
    \item Developed a multimodal fusion model for joint ASR and dialect identification (DID) (\textbf{4.65\% CER and 81.63\% DID accuracy}), integrating speech and text embeddings for Indian dialects~\cite{Saurabh_IS25}.
    
    \item Led the first large-scale study on DID in Indian languages (\textbf{79.81\% accuracy across 33 dialects})~\cite{ICASSP25_DID}.
    
    \item Enhanced low-resource ASR via adapter-based domain adaptation, reducing \textbf{WER (10\%-30\%)} and \textbf{CER (3\%-18\%)} across 9 languages~\cite{IS24_ASR}.
    
    \item Proposed a Gated Multi-Encoder ASR model with frame-level gating, reducing \textbf{WER by 7.5\% (Bhojpuri) and 9\% (Bengali)}~\cite{ASRU23_RESPIN}.
  \end{itemize}

  \item \href{https://syspin.iisc.ac.in/}{\textbf{SYSPIN}}: \textit{Text-to-Speech Synthesizer in Nine Indian Languages} \\
  Publications: \cite{LIMMITS24_OJSP2025}
  \begin{itemize}
    \item Developed a data filtering pipeline using Kaldi-based ASR models, improving corpus quality.
  \end{itemize}
\end{itemize}

\textbf{ARTPARK, IISc Bangalore, India} \hfill Sep 2022\textendash Present \\
Machine Learning/Signal Processing Consulting Engineer \\
Project: 
\begin{itemize}
\item \href{https://vaani.iisc.ac.in/}{\textbf{VAANI}}: \textit{Capturing the language landscape for an inclusive digital India}
\begin{itemize}
  \item Contributing to the developement of large-scale speech and text corpora covering \textbf{773 Indian districts}.
  \item Designed automated data pipelines for quality checks using signal processing and ML techniques.
\end{itemize}
\end{itemize}

\textbf{Department of ECE, NIT Patna, India} \hfill July 2019\textendash June 2020, Dec 2020\textendash June 2021 \\
Undergraduate Student Researcher \\
Advisor: Dr. S. Shahanawazuddin \\
Publications: ~\cite{Syed2021_APAC, Syed2021_DSP}
\begin{itemize}
  \item Investigated formant-modification and bispectrum-based front-end features to improve children’s ASR under zero-resource conditions~\cite{Syed2021_APAC}.
  \item Developed a CGAN-based voice conversion framework, transforming adult speech into child-like speech for ASR adaptation~\cite{Syed2021_DSP}.
\end{itemize}

\textbf{EICT Academy, IIT Guwahati, India} \hfill May 2019\textendash June 2019 \\
Summer Intern
\begin{itemize}
  \item Designed Verilog code for a 5-stage discrete wavelet transform cascade filter bank for FPGA-based simulation.
\end{itemize}

\section{Mentorship \& Professional Services}

\textbf{Reviewer:} ICASSP 2024, ICASSP 2025, IJCNN 2025.  

\textbf{Organizer:}  
\begin{itemize}
    \item \textbf{ICASSP 2024 (LIMMITS’24):} Co-organized session on Indic TTS, developed baselines.
    \item \textbf{ASRU 2023 (MADASR):} Led data curation, ASR baselines for Bengali, Bhojpuri.
    \item \textbf{Interspeech 2022 (Gram Vaani ASR):} Organized Hindi ASR challenge, developed Kaldi baselines.
\end{itemize}

\textbf{Student Volunteer:} ICASSP 2024, ICASSP 2025.  
  

\section{Awards}
\textbf{SLT-CODE Hackathon Winner 2022} – Won \textbf{Best Hackathon Project} Award for developing dialectal ASR systems for Bengali and Bhojpuri, presented at \textbf{SLT 2022}.


\printbibliography[title=\textbf{Selected Publications}]

\section{Languages and Skills}
\begin{minipage}{0.48\textwidth}
    \textbf{Languages}
    \begin{itemize}
        \item \textbf{Programming:} Python, Bash, PHP
        \item \textbf{Natural:} Bhojpuri, English, Hindi, Maithili
        % \item \textbf{TOEFL:} 94 (Reading: 23, Listening: 26, Speaking: 23, Writing: 22)
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
    \textbf{Skills}
    \begin{itemize}
        \item \textbf{ML/DL Toolkits:} PyTorch, Scikit-learn
        \item \textbf{ASR Frameworks:} ESPnet, Kaldi, Fairseq
        \item \textbf{Others:} MATLAB, Audacity, Praat, Git
    \end{itemize}
\end{minipage}

\end{document}
