\section{Education}

\textbf{B.Tech. in Electronics and Communication Engineering} \hfill 2016\textendash 2020 \\
National Institute of Technology, Patna \\
GPA: 7.42/10.00
\begin{itemize}
    \item \textbf{Capstone Project:} "Simulation of Hybrid Plasmonic Waveguides Based Devices and Its Applications"
    \begin{itemize}
        \item \textbf{Description:} Conducted simulations and analyzed the characteristics of various hybrid plasmonic waveguide-based devices using COMSOL Multiphysics software.
        \item \textbf{Advisor:} Dr. R. Ranjan
    \end{itemize}
\end{itemize}

\section{Experience}

\textbf{Research Associate} \hfill July 2021\textendash Present \\
SPIRE Lab, IISc Bangalore, India \\
Advisor: Prof. Prasanta Kumar Ghosh \\
Projects:
\begin{itemize}
  \item \textit{Speech Recognition in Agriculture and Finance for the Poor in India (RESPIN)} \\
  Publications: \cite{ICASSP25_DID, IS24_ASR, ASRU23_RESPIN, SPECOM23_RESPIN}
  \begin{itemize}
    \item Primarily involved in improving dialectal automatic speech recognition (ASR) in Indian languages.
    \item Working on multimodal, multitask approaches to improve dialect identification in Indian languages.
    \item Exploring the effect of auxiliary tasks such as dialect and domain identification on ASR.
    \item Conducted a comprehensive study on the impact of dialect and domain-specific statistical language models on ASR in Indian languages.
  \end{itemize}
  
  \item \textit{Text-to-speech synthesizer in nine Indian languages (SYSPIN)} \\
  Publications: \cite{SPECOM23_SYSPIN}
  \begin{itemize}
    \item Developed an efficient pipeline using Kaldi-based ASR models to filter out poorly aligned/transcribed data, contributing to the quality assessment of the SYSPIN data.
  \end{itemize}
\end{itemize}

\textbf{Machine Learning/Signal Processing Consulting Engineer} \hfill September 2022\textendash Present \\
ARTPARK, IISc Bangalore, India \\
Project: Development and Curation of Speech and Text Corpora for \href{https://vaani.iisc.ac.in/}{VAANI} \\
\begin{itemize}
  \item Playing a pivotal role in developing and curating extensive speech and text corpora covering 773 districts in India for the VAANI project, funded by Google.
  \item Employing signal processing and machine learning techniques to create an efficient data pipeline, ensuring data quality and accuracy in the VAANI project.
  \item Contributing to the success of the VAANI initiative by maintaining the highest standards of data quality.
\end{itemize}

\textbf{Undergraduate Student Researcher} \hfill July 2019\textendash June 2020, December 2020\textendash June 2021 \\
Department of ECE, NIT Patna, India \\
Advisor: Dr. S. Shahanawazuddin \\
Publications: ~\cite{Syed2021_DSP, Syed2021_APAC}
\begin{itemize}
  \item Explored front-end acoustic feature enhancement techniques to improve children's speech recognition in noisy and low-resource conditions~\cite{Syed2021_DSP}.
  \item Developed robust children's speech recognition systems in low-resource conditions and investigated the effect of formant scaling-based data augmentation on children's speaker verification systems~\cite{Syed2021_APAC}.
\end{itemize}

\textbf{Summer Intern} \hfill May 2019\textendash June 2019 \\
EICT Academy, IIT Guwahati, India \\
Advisor: Dr. Gaurav Trivedi \\
Project: Cascade filter bank implementation of discrete wavelet transform \\
\begin{itemize}
  \item Designed Verilog code for a 5-stage cascade filter bank structure of the discrete wavelet transform for FPGA-based simulation, gaining valuable insights into FPGA simulation.
\end{itemize}

\section{Conferences and Workshops}

\textbf{Reviewer for International Conferences}
\begin{itemize}
  \item \textbf{ICASSP 2024, ICASSP 2025, IJCNN 2025} – Reviewed research papers in speech processing, machine learning, and neural networks.
\end{itemize}

\textbf{LIMMITS'24 Challenge - ICASSP 2024}
\begin{itemize}
  \item Co-hosted a special session on \textit{LIMMITS'24: Multi-speaker, Multi-lingual Indic TTS with voice cloning} at ICASSP 2024, Seoul.
  \item Contributed to data curation and baseline model development.
\end{itemize}

\textbf{MADASR Challenge - ASRU 2023}
\begin{itemize}
  \item Organizing team member for the Model Adaptation for ASR in Low-Resource Indian Languages challenge.
  \item Contributed to data curation and baseline ASR models in Bengali and Bhojpuri.
\end{itemize}

\textbf{SLT-CODE Hackathon 2022}
\begin{itemize}
  \item \textbf{Best Hackathon Project Award} for dialectical speech recognition in Bengali and Bhojpuri.
  \item Developed Kaldi-based ASR models and curated training/testing data.
  \item Presented findings at SLT 2022.
\end{itemize}

\textbf{Gram Vaani ASR Challenge - Interspeech 2022}
\begin{itemize}
  \item Organizing team member; contributed to curating and open-sourcing a 1100-hour Hindi ASR corpus.
  \item Developed and open-sourced Kaldi-based ASR baseline models~\cite{bhanushali22_interspeech}.
\end{itemize}


\printbibliography[title=Publications]